Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
predators and refs

## Predator avoidance
Predator avoidance could also contribute to swimming behaviour of caribou
(Miller 2002). During calving, female caribou are known to swim to small islands
in freshwater lakes give birth, or with their calves after birth, to avoid
predation (Bergerud & Page 1987). The use of shoreline habitat in summer is
considered an effective anti-predator calving strategy by allowing for swimming
to islands or peninsulas as a predation avoidance flight response (Bergerud et
al. 1990). The use of water, and by association occasionally swimming, is
therefore part of the fine-scale interactions between caribou and their
predators and the use of islands appears to be an effective anti-predator
strategy.

>>>>

## Predator avoidance
Predator avoidance could also contribute to swimming behaviour of caribou
(Miller 2002). During calving, female caribou are known to swim to small islands
in freshwater lakes give birth, or with their calves after birth, to avoid
predation [@Bergerud_1987]. The use of shoreline habitat in summer is considered
an effective anti-predator calving strategy by allowing for swimming to islands
or peninsulas as a predation avoidance flight response [@Bergerud_1990]. The use
of water, and by association occasionally swimming, is therefore part of the
fine-scale interactions between caribou and their predators and the use of
islands appears to be an effective anti-predator strategy.
